---
title: "Barcode collisions "
output: github_document
---

```{r, include=FALSE}
library(tidyverse)
```

This document lists barcode collisions between Nextera primers and  NEXTFLEX Unique Dual Index Barcodes (Set D, adapters 289-384). Barcode pairs listed below should not be included on the same sequencing lane.

# i7 barcode collisions
Barcode collisions are ordered by the NEXTFLEX id at left, or the Nextera id at right.
```{r, comment=FALSE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
i7 <- read_csv("../indexDistances/i7_distances.csv", show_col_types = F) %>% 
  filter(hamming < 3) %>% select(-seqlev) %>%
  separate(col = Nextera_i7, into = c("tmp1", "tmp2"), sep = "\\.") %>%
  mutate(tmp2 = str_pad(tmp2, width = 3, side = "left", pad = "0")) %>%
  unite(col = Nextera_i7, tmp1:tmp2, sep = ".")

bind_cols(i7 %>% arrange(NEXTFLEX_ID),
          i7 %>% arrange(Nextera_i7)) %>% mutate(empty = "") %>% relocate(empty, .after = 3) %>%
  knitr::kable(
    col.names = c(
      "NEXTFLEX_ID",
      "Nextera_i7",
      "Hamming Distance",
      "",
      "NEXTFLEX_ID",
      "Nextera_i7",
      "Hamming Distance"
    ),
    caption = str_c(
      tally(i7),
      "i7 barcode pairs fail to meet a minimal Hamming distance of greater than 2.",
      sep = " "
    )
  )
```

# i5 barcode collisions
Barcode collisions are ordered by the NEXTFLEX id at left, or the Nextera id at right.
```{r, comment=FALSE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
i5 <- read_csv("../indexDistances/i5_distances.csv", show_col_types = F) %>% 
  filter(hamming < 3) %>% select(-seqlev) %>%
  separate(col = Nextera_i5, into = c("tmp1", "tmp2"), sep = "\\.") %>%
  mutate(tmp2 = str_pad(tmp2, width = 3, side = "left", pad = "0")) %>%
  unite(col = Nextera_i5, tmp1:tmp2, sep = ".")

bind_cols(i5 %>% arrange(NEXTFLEX_ID),
          i5 %>% arrange(Nextera_i5)) %>% mutate(empty = "") %>% relocate(empty, .after = 3) %>%
  knitr::kable(
    col.names = c(
      "NEXTFLEX_ID",
      "Nextera_i5",
      "Hamming Distance",
      "",
      "NEXTFLEX_ID",
      "Nextera_i5",
      "Hamming Distance"
    ),
    caption = str_c(
      tally(i5),
      "i5 barcode pairs fail to meet a minimal Hamming distance of greater than 2.",
      sep = " "
    )
  )
```

